---
title: "rtweet tutorial"
author: "Chris Dinsmore"
date: "5/18/2020"
output: html_document
---

---
output:
  word_document: default
  pdf_document: default
  html_document: default
---
#Chris Dinsmore
#using RTweet to pull Twitter Data
# See https://rtweet.info/index.html
#Addiitonal References and Recipes  https://rud.is/books/21-recipes/


#Add Packages

```{r, include=FALSE}
library(rtweet)
library(dplyr)
library(tidyverse)
library(RODBC)
library(DBI)
library(RSQLite)
library(rtweet) 
library(tidyr)
library(igraph)
library(hrbrthemes)
library(ggraph)
library(elasticsearchr)
library(ggplot2)
library(maps)
library("httpuv")
library("maps")

````


#Load package "httpuv" and Twitter Api
#Connect to Twitter Api
######Must Creat Titter App Before Projeding#####
#Creat Twitter APP https://rtweet.info/articles/auth.html
######Must Creat Titter App Before Projeding#####

```{r, include=TRUE}

## install httpuv if not already
if (!requireNamespace("httpuv", quietly = TRUE)) {
  install.packages("httpuv")
}

## load rtweet
library(rtweet)

## store api keys (these are fake example values; replace with your own keys)
api_key <- "enter api key here"
api_secret_key <- "enter api secret key here"

## authenticate via web browser
token <- create_token(
  app = "enter name of app here",
  consumer_key = api_key,
  consumer_secret = api_secret_key)


````


#Set WD
```{r, include=FALSE}
setwd("enter working directory")
getwd()
```



#Grab trends avaialble

```{r, include=TRUE}

rtweet::trends_available()
rtweet::get_trends()
````


#Get Trends by geographics

```{r, include=TRUE}
ww_trends <- get_trends('worldwide')
```



#Top Trends

```{r, include=TRUE}

glimpse(ww_trends)
```

# pull 10000 tweets that used the "#Covid19" hashtag and Map
#Will Need Google Maps API Key https://developers.google.com/maps/documentation/javascript/get-api-key
#Must use console to select 1: Yes



```{r, include=TRUE}

(Covid19 <- search_tweets("#Covid19", geocode = lookup_coords("United States"), n=10000, is_retweet = FALSE, 
                         retryonratelimit = FALSE)) 
#Add Lat & Long then create map plot
Covid19 <- lat_lng(Covid19)

par(mar = c(0, 0, 0, 0))
maps::map("state", lwd = .25)

with(Covid19, points(lng, lat, pch = 20, cex = .75, col = rgb(0, .3, .7, .75)))
````


#Create Time Series
```{r, include=TRUE}
#Create Time Series
ts_data(Covid19)
ts_plot(Covid19)
````




#Clean data by remove unnecasry columns
````{r, include=TRUE}
CV1 <- Covid19 %>% select('user_id', 'created_at', 'is_retweet', 'screen_name', 'text', 'source', 'favorite_count', 'retweet_count', 'hashtags', 'media_type', 'location', 'followers_count', 'friends_count', 'favourites_count', 'lat', 'lng', 'lang')
````

```{r, include=TRUE}
view(CV1)
summary(CV1)
```


#As a Matrix As Character

````{r, include=TRUE}
CV1 <- as.data.frame(CV1)
CV1 <- apply(CV1,2,as.character)
````


#Write to CSV

```{r, include=TRUE}

write.csv(CV1, 'CV1.csv')

````






